\thetitle

### 2018-01-07 TeX/manuscript.tex
added tikz diagram, found some papers for reference, and added some notes/questions regarding the project as a whole

\maketitle
\newpage
\tableofcontents
\newpage

@@

\begin{figure}

@@

	Numerical information consists of numerical values, such that there exists infinitely many numerical values between two numbers. This property makes numerical information continuous. In contrast, categorical information involves individual values out of a set of either finite or infinite possible values. Categorical information are discrete, however, so there exists a finite number of categories between any two categories. //

@@

	Information is represented in one of two ways, numerical or categorical. Numerical values give us the ability to identify the distance between two values, and to have an infinite number of possible values to work with. Categorical values allow us to express information where a specific value to represent the distance between two categories isn't appropriate. We can also express more vague values using categories, without the need for specific numerical values.
	We can express the speed that an object is moving using either numerical or categorical values. For instance, we may say that an object is moving at exactly 50 miles per hour, or we can simply say that the object is moving 'fast'. In the following figure, we will examine a situation in which both representations are necessary.

\begin{figure}

@@

@@

>>>>

\maketitle

\newpage
\tableofcontents
\newpage

@@

\begin{figure}
\centering
\begin{tikzpicture}

@@

	Numerical information consists of numerical values, such that there exists infinitely many numerical values between two numbers. This property makes numerical information continuous. In contrast, categorical information involves individual values out of a set of either finite or infinite possible values. Categorical information are discrete, however, so there exists a finite number of categories between any two categories.

@@

	Information is represented in one of two ways, numerical or categorical. Numerical values give us the ability to identify the distance between two values, and to have an infinite number of possible values to work with. Categorical values allow us to express information where a specific value to represent the distance between two categories isn't appropriate. We can also express more vague values using categories, without the need for specific numerical values.
	We can express the speed that an object is moving using either numerical or categorical values. For instance, we may say that an object is moving at exactly 50 miles per hour, or we can simply say that the object is moving 'fast'. In the following figures, we will examine how to convert between the two types.

	\node[value] (ObjectSpeed) at (0,-2) {Object's speed};
	\node[value] (Speed) at (0,0) {20 mph};

	\node[operation] (greaterThan) at (2,2.5) {compare op: $>=$};

	\node[value] (SpeedComp) at (4,0) {10 mph};

	\node[function] (If) at (5,5) {If};

	\node[function] (Return1) at (6.5,2.5) {return};
	\node[value] (Fast) at (6.5,0) {'Fast'};

	\node[function] (Return2) at (8.5,2.5) {return};
	\node[value] (Slow) at (8.5,0) {'Slow'};

	\draw[->](ObjectSpeed) -> (Speed)  node[midway,sloped,above] {};

	\draw[->](Speed) -> (greaterThan)  node[midway,sloped,above] {};
	\draw[->](SpeedComp) -> (greaterThan)  node[midway,sloped,above] {};

	\draw[->](greaterThan) -> (If)  node[midway,sloped,above] {condition};

	\draw[->](If) -> (Return1)  node[midway,sloped,above] {if true};	
	\draw[->](If) -> (Return2)  node[midway,sloped,above] {if false};

	\draw[->](Return1) -> (Fast)  node[midway,sloped,above] {};	
	\draw[->](Return2) -> (Slow)  node[midway,sloped,above] {};

@@

\caption{A syntax tree that defines a procedure for converting categorical representations to numerical ones. In this case, a threshold of 10mph is defined to detirmine whether a numerical definition of the speed of an object is 'Fast' or 'Slow' depending on whether or not the object's speed is above or below the threshold.}

@@

The threshold used in the above procedure is arbitrary, and can be defined differently in different networks. \textcolor{red} {This idea can be used to create a network where this threshold is optimized through gradient descent (similarly to the ReLu activation function with a variable bias)}

\textcolor{red} {Next Step? figure out how to convert from categorical to numerical.}
